---
title: "Escapeement Goals Evaluation Exercise"
author: "Chris Pike"
date: "October 17, 2018"
output: html_document
---

##Download Libraries

```{r,warning=F, message=F}
library(dplyr)
library(tidyr)
library(DT)
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# prepare daily escapment data

Daily data sourced from [Andrew Munro and Eric Volk. 2017. Summary of Pacific Salmon Escapement Goals in Alaska with a Review of Escapements from 2007 to 2015. Knowledge Network for Biocomplexity. doi:10.5063/F1TQ5ZRG.](doi:10.5063/F1TQ5ZRG)

+ filter for Bristol Bay Sockeye
+ summarize by year, calculating total count

```{r}
escapement_counts = read.csv(url("https://knb.ecoinformatics.org/knb/d1/mn/v2/object/urn%3Auuid%3Af119a05b-bbe7-4aea-93c6-85434dcb1c5e",method = "libcurl"),
                    stringsAsFactors = FALSE)
head(escapement_counts)
#unique(escapement_counts$SASAP.Region)
```

```{r}
escapement_BB_Sockeye <- escapement_counts %>% 
  #filter for only Bristol Bay Sockeye
  filter(SASAP.Region == "Bristol Bay", Species == "Sockeye")
  head(escapement_BB_Sockeye)

```

```{r}
escapement_BB_Sockeye_cleaned <- escapement_BB_Sockeye %>% 
  #get rid of unnecesary columns
  select(Location, sampleDate, DailyCount) %>% 
  separate(sampleDate, c("year", "month", "day"), sep = "-") %>% 
  group_by(Location, year) %>% 
  summarise(escapement = sum(DailyCount))
tail(escapement_BB_Sockeye_cleaned)
```

```{r}


```



```{r}
escapement_goals = read.csv(url("https://knb.ecoinformatics.org/knb/d1/mn/v2/object/knb.92014.1",method = "libcurl"),
                    stringsAsFactors = FALSE)
head(escapement_goals)
#unique(escapement_goals$Region)
```

```{r}
BB_sockeye_goals <- escapement_goals %>%
  filter(Species == "Sockeye", Region == "Bristol Bay") %>% 
  mutate(Lower = as.numeric(Lower), Initial.Year = as.numeric(Initial.Year))
  #unique(BB_sockeye_goals$Region)
head(BB_sockeye_goals)
  
  
  
  
```
```{r}
#join the tables


```



# prepare escapement goals data

# Evaluate escapement goals